\begin{longtable}{p{2.8cm}p{2.9cm}cccp{1.9cm}p{6.0cm}}
\caption{Predictor screening across all candidate panel columns}\label{tab:predictor_screening}\\
\toprule
Variable & Source & First & Last & Obs & Status & Reason \\
\midrule
\endfirsthead
\multicolumn{7}{l}{\textit{Continued from previous page}}\\
\toprule
Variable & Source & First & Last & Obs & Status & Reason \\
\midrule
\endhead
\midrule
\multicolumn{7}{r}{\textit{Continued on next page}}\\
\endfoot
\bottomrule
\multicolumn{7}{p{0.94\textwidth}}{\footnotesize Candidate columns are the 26 non-date fields in the merged forecasting panel. Status distinguishes dependent variables retained in the main horse race, appendix-only robustness variables, and excluded series. Quarterly debt and IIP series are forward-filled in the merged panel before the forecasting-stage missing-data rule is applied.}\\
\endlastfoot
Gross reserves & Gross Reserves (Compiled) & 2005:01 & 2025:12 & 252 & Target & Dependent variable in every specification. \\
Import cover & Gross Reserves (Compiled) & 2005:01 & 2025:12 & 252 & Excluded & Reserve-adequacy ratio, not a forecasting regressor. \\
FX reserves & Reserve Assets (CBSL Official) & 2013:11 & 2025:12 & 146 & Excluded & Reserve subcomponent with short 2013+ coverage and mechanical overlap with the target. \\
IMF reserve position & Reserve Assets (CBSL Official) & 2013:11 & 2025:12 & 146 & Excluded & Reserve subcomponent with short coverage and mechanical overlap with the target. \\
SDRs & Reserve Assets (CBSL Official) & 2013:11 & 2025:12 & 146 & Excluded & Reserve subcomponent with short coverage and mechanical overlap with the target. \\
Gold holdings & Reserve Assets (CBSL Official) & 2013:11 & 2025:12 & 146 & Excluded & Reserve subcomponent dominated by valuation effects and short 2013+ coverage. \\
Exports & Merchandise Exports & 2007:01 & 2025:11 & 224 & Main text & Core gross-flow inflow; retained in BoP, PCA, and Full sets. \\
Imports & Merchandise Imports & 2007:01 & 2025:11 & 225 & Main text & Core gross-flow outflow; retained in BoP, PCA, and Full sets. \\
Tourism earnings & Tourism Earnings & 2009:01 & 2024:12 & 192 & Main text & Sri Lanka-specific external revenue channel; retained in BoP and Full sets. \\
Remittances & Workers' Remittances & 2009:01 & 2025:10 & 202 & Main text & Stable FX inflow; retained in BoP, PCA, and Full sets. \\
CSE net flows & CSE Portfolio Flows & 2012:01 & 2025:11 & 166 & Appendix only & Monthly capital-flow proxy used in omitted-variable robustness; excluded from the main horse race to preserve the longer baseline window. \\
Reserve money (M0) & Monetary Aggregates (M0, M2) & 2005:01 & 2025:03 & 217 & Excluded & Reserve money alternative considered but M2 aligns more directly with the reserve-adequacy literature. \\
Broad money (M2, LKR) & Monetary Aggregates (M0, M2) & 2005:01 & 2025:03 & 217 & Excluded & Converted to USD and represented by m2\_usd\_m in the main specifications. \\
USD/LKR & Exchange Rate (USD/LKR) & 2005:01 & 2025:12 & 252 & Main text & Exchange-rate intervention channel; retained in Parsimonious, Monetary, and Full sets. \\
Inflation (YoY) & NCPI Inflation & 2019:01 & 2024:11 & 71 & Excluded & Only 71 usable observations in the merged panel, too short for the baseline horse race. \\
Govt short-term debt (USD) & External Debt (USD) & -- & -- & 0 & Excluded & All missing in the merged monthly panel. \\
Total short-term debt (USD) & External Debt (USD) & -- & -- & 0 & Excluded & All missing in the merged monthly panel. \\
Portfolio liabilities & Int'l Investment Position & 2012:12 & 2025:12 & 157 & Appendix only & Liability proxy from the IIP used in the omitted-variable appendix; shorter 2012+ coverage keeps it out of the main text sets. \\
Short-term debt (LKR) & Central Government Debt & 2005:12 & 2025:12 & 241 & Appendix only & Debt-pressure proxy used in omitted-variable robustness after USD conversion; shorter coverage keeps it out of the main text sets. \\
Trade balance & Derived: exports minus imports & 2007:01 & 2025:11 & 224 & Main text & Aggregate current-account proxy retained in Parsimonious and Full sets. \\
Current-account proxy & Derived: exports + remittances + tourism - imports & 2005:01 & 2025:12 & 252 & Excluded & Linear combination of BoP components already tested separately; excluded to avoid double counting. \\
Net usable reserves & Derived: gross reserves less PBOC swap & 2005:01 & 2025:12 & 252 & Excluded & Alternative reserve target, not an explanatory predictor. \\
Guidotti-Greenspan ratio & Derived: gross reserves / short-term debt & -- & -- & 0 & Excluded & Unavailable because the USD short-term debt denominator is missing in the merged panel. \\
Broad money (M2, USD) & Derived: M2 in LKR / USDLKR & 2005:01 & 2025:03 & 217 & Main text & Monetary/liquidity proxy retained in Monetary, PCA, and Full sets. \\
Reserve change & Derived: first difference of gross reserves & 2005:02 & 2025:12 & 251 & Excluded & Transformation of the dependent variable used for diagnostics and state equations, not as a standalone predictor. \\
Reserve change (\%) & Derived: pct change of gross reserves & 2005:02 & 2025:12 & 251 & Excluded & Target transformation only. \\
\end{longtable}